Identity Blockchain - Proof of Identity

### 2022-07-09 paper.tex
updated README
none

@@

\title{Identity Blockchain - Proof of Identity}
\author{
Albert Vučinović, University North\\
Miroslav Jerković, University of Zagreb
}
\begin{document}
\maketitle

@@

  function registerKid(
    uint256 hNin, // hNin = H(Nin)
    uint256 vKid, // vKid = KidPrivate("registerKid")
    bytes proofNinOwnsKid
  ) public {
    uint256 previousKey = ninKidUsed[hNin];
    if (previousKey == vKid) return; // already registered
    bool isOwner = zksnarkverify(VK, [hNin, vKid], proofNinOwnsKid); // VK = verification key
    if (isOwner && !kidInvalid[vKid]) {
      if (previousKey != 0) kidInvalid[previousKey] = true;
      ninKidUsed[hNin] = vKid;
    }
  }
\end{lstlisting}
\xdef\tpd{\the\prevdepth}
\end{minipage}
\item[] \underline{Features}
    \begin{itemize}
      \item[] \textbf{Sybil resistance} \\ A Person is prevented from registering more than one $\khk$, e.g. by using different identification documents issued for the same $Nin$.
          \vspace{5px}
      \item[] \textbf{Fix for the loss of eID} \\ A Person who has lost a previously registered $\kid$, e.g. due to loss of eID, can overwrite it by registering a new $\kid$.
          \vspace{5px}
      \item[] \textbf{Identity theft damage control} \\ If a Person overwrites the previous $\kid$ with a new one, the identity Thief loses access to services that verify the entire identity chain.
    \end{itemize}

>>>>

\lstdefinelanguage{circom}{
	keywords=[1]{signal, input, output, public, template, component, var, function, return, if, else, for, while,
		do, log, assert, include, pragma, circom}, % generic keywords including crypto operations
	keywordstyle=[1]\color{blue}\bfseries,
	keywords=[2]{},	% types; money and time units
	keywordstyle=[2]\color{teal}\bfseries,
	keywords=[3]{},	% environment variables
	keywordstyle=[3]\color{violet}\bfseries,
	identifierstyle=\color{black},
	sensitive=false,
	comment=[l]{//},
	morecomment=[s]{/*}{*/},
	commentstyle=\color{gray}\ttfamily,
	stringstyle=\color{red}\ttfamily,
	morestring=[b]',
	morestring=[b]"
}

\lstset{
	language=circom,
	backgroundcolor=\color{verylightblue},
	extendedchars=true,
	basicstyle=\footnotesize\ttfamily,
	showstringspaces=false,
	showspaces=false,
	numbers=left,
	numberstyle=\footnotesize,
	numbersep=9pt,
	tabsize=2,
	breaklines=true,
	showtabs=false,
	captionpos=b
}

@@

\title{Identity Blockchain - Proof of Identity}
\author{
Albert Vučinović, University North\\
Miroslav Jerković, University of Zagreb}
\begin{document}
\maketitle

@@

  function registerKid(
    uint256 hNin, // hNin = H(Nin)
    uint256 vKid, // vKid = KidPrivate("registerKid")
    bytes proofNinOwnsKid
  ) public {
    uint256 previousKey = ninKidUsed[hNin];
    if (previousKey == vKid) return; // already registered
    bool isOwner = zksnarkverify(VK, [hNin, vKid], proofNinOwnsKid); // VK = verification key
    if (isOwner && !kidInvalid[vKid]) {
      if (previousKey != 0) kidInvalid[previousKey] = true;
      ninKidUsed[hNin] = vKid;
    }
  }
\end{lstlisting}
\xdef\tpd{\the\prevdepth}
\end{minipage}

\item[] \underline{Pseudo-circom code}

\hfill\begin{minipage}{\dimexpr\textwidth-20px}
\begin{lstlisting}[language=circom]
pragma circom 2.0.0;

template NinOwnsKid(){
	//TODO: What happens to uint256 when converted to signal

	//public:
	signal input hNin;
	signal input vKid;

	//private:

	//Take Kid
	//Take CA

}
component main { public [hNin,vKid]} = NinOwnsKid();
\end{lstlisting}
\xdef\tpd{\the\prevdepth}
\end{minipage}

\item[] \underline{Features}
    \begin{itemize}
      \item[] \textbf{Sybil resistance} \\ A Person is prevented from registering more than one $\khk$, e.g. by using different identification documents issued for the same $Nin$.
          \vspace{5px}
      \item[] \textbf{Fix for the loss of eID} \\ A Person who has lost a previously registered $\kid$, e.g. due to loss of eID, can overwrite it by registering a new $\kid$.
          \vspace{5px}
      \item[] \textbf{Identity theft damage control} \\ If a Person overwrites the previous $\kid$ with a new one, the identity Thief loses access to services that verify the entire identity chain.
    \end{itemize}
